Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-29 awipev-CO2.Rmd
Minor update
Update following changes from pco2-calc_insitu to pco2-calc_fb

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
#discrete_no_na$pco2_calc<- carb$pCO2

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
#discrete_is_na$pco2_calc<- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```

@@

# calculated pCO2 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, pco2_calc_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_insitu , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_insitu, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_insitu_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc_insitu, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc_insitu",
    label = "pco2_calc_insitu",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

@@

```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>%

@@

xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# calculate omeaga arag
z <- d_all %>% 
  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
oa_tbf <- as_tibble(
  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
                          ks = "d", pHscale = "T", b = "u74")
) %>% 
  dplyr::mutate(datetime = z$datetime,
                oa = OmegaAragonite) %>% 
dplyr::select(datetime, oa)
# select time series data and add Omega
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
                ph_dur_corr, pco2_calc_insitu, at_calc)
d <- left_join(d, oa_tbf, by = 'datetime')

@@

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
```
```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_insitu , nperm = 99)

p <-  ggplot(d, aes(x=pco2_calc_insitu, y= pco2_corr)) +
  geom_point(color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
  mytheme(size_labs = 10) +
    theme(aspect.ratio=1, plot.title = element_text(size=7))
ggsave(file="figures/pco2.png", p,  width = 14, height = 14, units = "cm")
```

@@

@@

[AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc_insitu: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script

>>>>

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```

@@

# calculated pCO2 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, pco2_calc_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_fb , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc_fb",
    label = "pco2_calc_fb",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

@@

```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))

@@

xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# calculate omeaga arag
z <- d_all %>% 
  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
oa_tbf <- as_tibble(
  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
                          ks = "d", pHscale = "T", b = "u74")
) %>% 
  dplyr::mutate(datetime = z$datetime,
                oa = OmegaAragonite) %>% 
dplyr::select(datetime, oa)
# select time series data and add Omega
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
                ph_dur_corr, pco2_calc_fb, at_calc)
d <- left_join(d, oa_tbf, by = 'datetime')

@@

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
```
```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_fb , nperm = 99)

p <-  ggplot(d, aes(x=pco2_calc_fb, y= pco2_corr)) +
  geom_point(color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
  mytheme(size_labs = 10) +
    theme(aspect.ratio=1, plot.title = element_text(size=7))
ggsave(file="figures/pco2.png", p,  width = 14, height = 14, units = "cm")
```

@@

[Logbook discrete sampling](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit#gid=1034421443)

@@

[AWI NRT database](https://dashboard.awi.de/data-xxl/), search for svluwobs

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script
